Verifying Spatial Properties of Stencil Computations

### 2016-11-15 paper.tex
Simplify syntax entry

Figure~\ref{fig:syntax} gives the syntax of stencil specifications,
which we introduce in stages below.  The top-level is given by the
\nonterm{specification} production which splits into either a
\nonterm{regionDec} (region declaration) or a \nonterm{specDec}
(specification declaration).

>>>>

Figure~\ref{fig:syntax} gives the syntax of stencil specifications, which is
detailed below. The entry point is the \nonterm{specification} production which
splits into either a \emph{region declaration} or a \emph{specification
declaration}.
